---
title: "Discurso presidencial de 1996"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cerulean
    social: ["facebook", "github", "menu"]
---

```{r setup, include=FALSE}
library(flexdashboard)
```  

# BIOGRAFIA {data-icon="fa-github"}

column {data-width=400}
---  
### Alberto Fujimori  

To include a value box within a Shiny flexdashboard you need to be sure to wrap the value box output in renderValueBox (so that it is updated when inputs it depends on change). For example:  

column {data-width=600}  
---  

### Foto de Fujimori  

  
# GRÁFICOS {data-icon="ion-ios-star-half"}  

Column {data-width=650 .tabset}
-----------------------------------------------------------------------

### Chart A

```{r}

```  

### Chart X
```{r}

```


Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```  

# Valuebox {data-orientation="rows" data-icon="ion-erlenmeyer-flask"}

## {data-height=300}  

### **VALUEBOX**  

```{r}
#valueBox(value = 17,
#         caption = "personas",
#        color = "orange")
```  

## {data-height=700}  

### **GRAFICAS DE SENTIMIENTO**  

```{r}

```








